Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

Once the sampling is obtained, the surrogate model is created. The Multivariate adaptive regression splines (MARS) method is chosen, where the surrogate functions are adjusted with cubic splines following the next expression
\begin{equation}\label{eq:mars}
\hat{f}\left ( \bm{x} \right )= \sum_{m=1}^{M}a_{m}B_{m}\left ( \bm{x} \right ),
\end{equation}
where $B_{m}$ are the power basis functions, $a_{m}$ the coefficients of the functions, and $M$ is the number of functions. This method is more thoroughly explained in \citep{Friedman1995197}.

@@

The methods selected for both the single- and the multi-objective optimization are the genetic algorithms from the JEGA Library, developed by \citet{JEGA}. This methods perform optimization supporting general constraints as well as mixtures of real and discrete variables. The variables are encoded and referred to as chromosomes, and each digit of the variable is a gene.

@@

The second reason for choosing these objective functions is purely computational. Traditionally, other researchers have swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \citep{Hou2007555}. The SEA function is defined as a ratio between $E_a$ and $m$:
\begin{equation}\label{SEA}
  S\! EA=\dfrac {E_a} {m}
\end{equation}

>>>>

Once the sampling is obtained, the surrogate model is created. The Multivariate adaptive regression splines (MARS) method is chosen, where the surrogate functions are adjusted with cubic splines following the next expression
\begin{equation}\label{eq:mars}
\hat{f}\left ( \bm{x} \right )= \sum_{m=1}^{M}a_{m}B_{m}\left ( \bm{x} \right ),
\end{equation}
where $B_{m}$ are the power basis functions, $a_{m}$ the coefficients of the functions, and $M$ is the number of functions. This method is more thoroughly explained in \cite{Friedman1995197}.

@@

The methods selected for both the single- and the multi-objective optimization are the genetic algorithms from the JEGA Library, developed by \cite{JEGA}. This methods perform optimization supporting general constraints as well as mixtures of real and discrete variables. The variables are encoded and referred to as chromosomes, and each digit of the variable is a gene.

@@

The second reason for choosing these objective functions is purely computational. Traditionally, other researchers have swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. The SEA function is defined as a ratio between $E_a$ and $m$:
\begin{equation}\label{SEA}
  S\! EA=\dfrac {E_a} {m}
\end{equation}
